Structured Versus Decorated Cospans

### 2022-04-05 cospans_compositionality_3.tex
added author addresses
added DOI to reference [7] as an example.
dois

@@

\author[1]{John C. Baez}
\author[2]{Kenny Courser}
\affil[1,2]{Department of Mathematics, University of California, Riverside CA, USA 92521}
\affil[1]{Centre for Quantum Technologies, National University of Singapore, Singapore 117543}
\author[3]{Christina Vasilakopoulou}
\affil[3]{Department of Mathematics, University of Patras, Greece 265 04}
%\email{baez@math.ucr.edu, kcour001@ucr.edu, cvasilak@math.upatras.gr}

@@

\bibitem{BFP} J.\ C.\ Baez, B.\ Fong and B.\ S.\ Pollard, A compositional framework for Markov processes, \textsl{Jour. Math. Phys.} \textbf{57} (2016), 033301. Available as \href{http://arxiv.org/abs/1508.06448}{arXiv:1508.06448}.

\bibitem{BM}  J.\ C.\ Baez and J.\ Master, Open Petri nets, \textsl{Math.\ Struct.\ Comput.\ Sci.\ }\textbf{30} (2020), 314--341. Available as 
\href{https://arxiv.org/abs/1808.05415}{arXiv:1808.05415}.

\bibitem{BP} J.\ C.\ Baez and B.\ S.\ Pollard, A compositional framework for chemical reaction networks, \textsl{Rev.\ Math.\ Phys.\ }\textbf{29} (2017), 1750028.  Available as \href{http://arxiv.org/abs/1704.02051}{arXiv:1704.02051}.

\bibitem{BFV} G.\ Bakirtzis, C.\ H.\ Fleming and C.\ Vasilakopoulou, Categorical semantics of cyber-physical systems theory. Available as 
\href{https://arxiv.org/abs/2010.08003}{arXiv:2010.08003}.

\bibitem{BSZ} F.\ Bonchi, P.\ Soboci\'nski and F.\ Zanasi, A categorical semantics of signal flow graphs, in \textsl{CONCUR 2014--Concurrency Theory}, eds.\ P.\ Baldan and D.\ Gorla, Lecture Notes in Computer Science \textbf{8704}, Springer, Berlin, 2014, pp.\ 435--450.  Available at \href{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}.

\bibitem{Borc} F. \ Borceux, \textsl{Handbook of Categorical Algebra}, vol.\ 2, 
Cambridge University Press, Cambridge, 1994.

%\bibitem{Brown1} R.\ Brown and C.\ B.\ Spencer, Double groupoids and crossed modules, 
%\textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{17} (1976), 343--362.

%\bibitem{Brown2} R.\ Brown, K.\ Hardie, H.\ Kamps and T.\ Porter, The homotopy double groupoid of a Hausdorff space, \textsl{Theory Appl.\ Categ.} \textbf{10} (2002), 71--93.

%\bibitem{Be} J.\ B\'enabou, Introduction to bicategories, in {\sl Reports
%of the Midwest Category Seminar}, Lecture Notes in Mathematics \textbf{47}, Springer, Berlin, 1967, pp.\ 1--77.

\bibitem{BungeFiore} M.\ Bunge and M.\ Fiore, Unique factorisation lifting functors and categories of linearly-controlled processes, \textsl{Math.\ Struct.\ Comput.\ Sci.\ } \textbf{10} (2000), 137--163.

%\bibitem{CC} D.\ Cicala and K.\ Courser, Spans of cospans in a topos. Available as \href{https://arxiv.org/abs/1707.02098}{arXiv:1707.02098}.

@@

\bibitem{CTF} G.\ Craciun, Y.\ Tang and M.\ Feinberg, Understanding bistability in complex enzyme-driven reaction networks, \textsl{PNAS} \textbf{103} (2006), 8697--8702.

\bibitem{DS} B.\ Day and R.\ Street, Monoidal bicategories and Hopf algebroids, \textsl{Adv.\ Math.} \textbf{129} (1997), 99--157.

%\bibitem{Ehresmann63} C.\ Ehresmann, Cat\'egories structur\'ees III: Quintettes et applications covariantes,  \textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{5} (1963), 1--22.

%\bibitem{Ehresmann65} C.\ Ehresmann, {\sl Cat\'egories et Structures,} Dunod, Paris, 1965.

@@

\bibitem{FRS} B.\ Fong, P.\ Rapisarda and P.\ Sobocinski, A categorical approach to open and interconnected dynamical systems, in \textsl{Proceedings of the 31st Annual ACM/IEEE Symposium on Logic in Computer Science (LICS)}, IEEE, New York, 2016, pp.\ 1--10.  Available as \href{http://arxiv.org/abs/510.05076}{arXiv:1510.05076}.

\bibitem{GiraultValk} C.\ Girault and R.\ Valk, \textsl{Petri Nets for Systems Engineering: a Guide to Modeling, Verification, and Applications}, Springer, Berlin, 2013.

\bibitem{GPS} R.\ Gordon, A.\ J.\ Power and R.\ Street, Coherence for tricategories, \textsl{Mem.\ Amer.\ Math.\ Soc.\ }\textbf{558}, 1995.

@@

\bibitem{Gray} J. \ Gray, Fibred and cofibred categories, in \textsl{Proceedings of the Conference on Categorical Algebra: La Jolla 1965}, eds.\ S.\ Eilenberg \textit{et al}, Springer, Berlin, 1966, pp.\ 21--83.

\bibitem{Haas} P.\ J.\ Haas, \textsl{Stochastic Petri Nets: Modelling, Stability, Simulation},
Springer, Berlin, 2002.

@@

\bibitem{Hermida1999} C. \ Hermida, Some properties of Fib as a fibred 2-category, \textsl{J.\ Pure Appl.\ Alg.\ } \textbf{134} (1999), 83--109.

\bibitem{Jacobs} B. \ Jacobs, \textsl{Categorical Logic and Type Theory}, Elsevier, Amsterdam, 1999.

\bibitem{JNW} A.\ Joyal, M.\ Nielsen and G.\ Winskel, Bisimulation from open maps, \textsl{Inf.\ Comput.\ }\textbf{127} (1996), 164--185.

@@

\bibitem{KS} G.\ M.\ Kelly and R.\ Street, Review of the elements of 2-categories, in \textsl{Category Seminar}, ed.\ G.\ M.\ Kelly, Lecture Notes in Mathematics \textbf{40}, Springer, Berlin, 1974, pp.\ 75--103.

\bibitem{Koch} I.\ Koch, Petri nets---a mathematical formalism to analyze chemical reaction
networks, \textsl{Mol.\ Inform.\  }\textbf{29} (2010), 838--843.

% \bibitem{LP} S.\ Lack and S.\ Paoli, 2-nerves for bicategories, \textsl{$K$-Theory} \textbf{38} (2008), 153--175.

@@

%\bibitem{LS} E.\ Lerman and D.\ Spivak, An algebra of open continuous time dynamical systems and networks. Available as \href{http://arxiv.org/abs/1602.01017}{arXiv:1602.01017}.

%\bibitem{Lack} S.\ Lack, Limits for lax morphisms, \textsl{Applied Categorical Structures} $\mathbf{30}$ (2005), 189--203. Available %at \href{http://maths.mq.edu.au/~slack/papers/talgl.pdf}{http://maths.mq.edu.au/$\sim$slack/papers/talgl.pdf}.

%\bibitem{Lerm} E.\ Lerman and D.\ Spivak, An algebra of open continuous time dynamical systems and networks. Available as %%\href{http://arxiv.org/abs/1602.01017}{arXiv:1602.01017}.

%   \bibitem{ML} S.\ Mac Lane, {\sl Categories for the Working Mathematician},
%     Springer, Berlin, 1998.

@@

%\bibitem{Panan} F.\ Clerc, H.\ Humphrey and P.\ Panangaden, Bicategories of Markov processes,  to appear.

@@

\bibitem{SSV} P.\ Schultz, D.\ Spivak and C.\ Vasilakopoulou, Dynamical systems and sheaves, \textsl{Appl.\ Cat.\ Struct.\ }\textbf{28} (2020), 1--57. Available as \href{https://arxiv.org/abs/1609.08086}{arXiv:1609.08086}.

@@

\bibitem{Wilkinson} D.\ J.\ Wilkinson, \textsl{Stochastic Modelling for Systems Biology},
Taylor and Francis, New York, 2006.

\bibitem{Willems} J.\ C.\ Willems, The behavioral approach to open and interconnected systems, \textsl{IEEE Control Systems Magazine} \textbf{27} (2007), 46--99.  Available as \href{https://citeseerx.ist.psu.edu/viewdoc/summary?doi=10.1.1.163.8131}{https://citeseerx.ist.psu.edu/viewdoc/summary?doi=10.1.1.163.8131}.

>>>>

% to get \begin{thm} and \end{thm} to work

@@

\author[1]{John C. Baez}
\email{baez@math.ucr.edu}
\author[2]{Kenny Courser}
\email{kcour001@ucr.edu}
\affil[1,2]{Department of Mathematics, University of California, Riverside CA, USA 92521}
\affil[1]{Centre for Quantum Technologies, National University of Singapore, Singapore 117543}
\author[3]{Christina Vasilakopoulou}
\email{cvasilak@math.upatras.gr}
\affil[3]{Department of Mathematics, University of Patras, Greece 265 04}
%\email{baez@math.ucr.edu, kcour001@ucr.edu, cvasilak@math.upatras.gr}

@@

\bibitem{BFP} J.\ C.\ Baez, B.\ Fong and B.\ S.\ Pollard, A compositional framework for Markov processes, 
\textsl{Jour. Math. Phys.} \textbf{57} (2016), 033301. 
\href{https://doi.org/10.1063/1.4941578}{https://doi.org/10.1063/1.4941578}. Available as 
\href{http://arxiv.org/abs/1508.06448}{arXiv:1508.06448}.

\bibitem{BM}  J.\ C.\ Baez and J.\ Master, Open Petri nets, \textsl{Math.\ Struct.\ Comput.\ Sci.\ }\textbf{30} (2020), 314--341. 
\href{https://doi.org/10.1017/s0960129520000043}{https://doi.org/10.1017/s0960129520000043}.
Available as 
\href{https://arxiv.org/abs/1808.05415}{arXiv:1808.05415}.

\bibitem{BP} J.\ C.\ Baez and B.\ S.\ Pollard, A compositional framework for chemical reaction networks, \textsl{Rev.\ Math.\ Phys.\ }\textbf{29} 
(2017), 1750028. \href{https://doi.org/10.1142/S0129055X17500283}{https://doi.org/10.1142/S0129055X17500283}.
Available as \href{http://arxiv.org/abs/1704.02051}{arXiv:1704.02051}.

\bibitem{BFV} G.\ Bakirtzis, C.\ H.\ Fleming and C.\ Vasilakopoulou, Categorical semantics of cyber-physical systems theory, \textsl{ACM Trans.\ 
Cyber-Phys.\ Syst.\ } \textbf{5} (2021). \href{https://doi.org/10.1145/3461669}{https://doi.org/10.1145/3461669}. Available as 
\href{https://arxiv.org/abs/2010.08003}{arXiv:2010.08003}.

\bibitem{BSZ} F.\ Bonchi, P.\ Soboci\'nski and F.\ Zanasi, A categorical semantics of signal flow graphs, in \textsl{CONCUR 2014--Concurrency Theory}, 
eds.\ P.\ Baldan and D.\ Gorla, Lecture Notes in Computer Science \textbf{8704}, Springer, Berlin, 2014, pp.\ 435--450. 
\href{https://doi.org/10.1007/978-3-662-44584-6\_30}{https://doi.org/10.1007/978-3-662-44584-6\_30}.  Available at 
\href{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}.

\bibitem{Borc} F. \ Borceux, \textsl{Handbook of Categorical Algebra}, vol.\ 2, 
Cambridge University Press, Cambridge, 1994. \href{https://doi.org/10.1017/CBO9780511525865}{https://doi.org/10.1017/CBO9780511525865}.

\bibitem{BungeFiore} M.\ Bunge and M.\ Fiore, Unique factorisation lifting functors and categories of linearly-controlled processes, \textsl{Math.\ 
Struct.\ Comput.\ Sci.\ } \textbf{10} (2000), 137--163. \href{https://doi.org/10.1017/S0960129599003023}{https://doi.org/10.1017/S0960129599003023}.

@@

\bibitem{CTF} G.\ Craciun, Y.\ Tang and M.\ Feinberg, Understanding bistability in complex enzyme-driven reaction networks, \textsl{PNAS} \textbf{103} 
(2006), 8697--8702. \href{https://doi.org/10.1073/pnas.0602767103}{https://doi.org/10.1073/pnas.0602767103}.

\bibitem{DS} B.\ Day and R.\ Street, Monoidal bicategories and Hopf algebroids, \textsl{Adv.\ Math.} \textbf{129} (1997), 99--157. 
\href{https://doi.org/10.1006/aima.1997.1649}{https://doi.org/10.1006/aima.1997.1649}.

@@

\bibitem{FRS} B.\ Fong, P.\ Rapisarda and P.\ Sobocinski, A categorical approach to open and interconnected dynamical systems, in \textsl{Proceedings 
of the 31st Annual ACM/IEEE Symposium on Logic in Computer Science (LICS)}, IEEE, New York, 2016, pp.\ 1--10. 
\href{https://doi.org/10.1145/2933575.2934556}{https://doi.org/10.1145/2933575.2934556}. Available as 
\href{http://arxiv.org/abs/510.05076}{arXiv:1510.05076}.

\bibitem{GiraultValk} C.\ Girault and R.\ Valk, \textsl{Petri Nets for Systems Engineering: a Guide to Modeling, Verification, and Applications}, 
Springer, Berlin, 2013. \href{https://doi.org/10.1007/978-3-662-05324-9}{https://doi.org/10.1007/978-3-662-05324-9}.

\bibitem{GPS} R.\ Gordon, A.\ J.\ Power and R.\ Street, Coherence for tricategories, \textsl{Mem.\ Amer.\ Math.\ Soc.\ }\textbf{558}, 1995. 
\href{https://doi.org/10.1090/memo/0558}{https://doi.org/10.1090/memo/0558}.

@@

\bibitem{Gray} J. \ Gray, Fibred and cofibred categories, in \textsl{Proceedings of the Conference on Categorical Algebra: La Jolla 1965}, eds.\ S.\ 
Eilenberg \textit{et al}, Springer, Berlin, 1966, pp.\ 21--83. 
\href{https://doi.org/10.1007/978-3-642-99902-4\_2}{https://doi.org/10.1007/978-3-642-99902-4\_2}.

\bibitem{Haas} P.\ J.\ Haas, \textsl{Stochastic Petri Nets: Modelling, Stability, Simulation},
Springer, Berlin, 2002. \href{https://doi.org/10.1007/b97265}{https://doi.org/10.1007/b97265}.

@@

\bibitem{Hermida1999} C. \ Hermida, Some properties of Fib as a fibred 2-category, \textsl{J.\ Pure Appl.\ Alg.\ } \textbf{134} (1999), 83--109. 
\href{https://doi.org/10.1016/S0022-4049(97)00129-1}{https://doi.org/10.1016/S0022-4049(97)00129-1}.

\bibitem{Jacobs} B. \ Jacobs, \textsl{Categorical Logic and Type Theory}, Elsevier, Amsterdam, 1999. 
\href{https://doi.org/10.2307/421214}{https://doi.org/10.2307/4212146}.

\bibitem{JNW} A.\ Joyal, M.\ Nielsen and G.\ Winskel, Bisimulation from open maps, \textsl{Inf.\ Comput.\ }\textbf{127} (1996), 164--185. 
\href{https://doi.org/10.1006/inco.1996.0057}{https://doi.org/10.1006/inco.1996.0057}.

@@

\bibitem{KS} G.\ M.\ Kelly and R.\ Street, Review of the elements of 2-categories, in \textsl{Category Seminar}, ed.\ G.\ M.\ Kelly, Lecture Notes in 
Mathematics \textbf{40}, Springer, Berlin, 1974, pp.\ 75--103. \href{https://doi.org/10.1007/BFb0063101}{https://doi.org/10.1007/BFb0063101}.

\bibitem{Koch} I.\ Koch, Petri nets---a mathematical formalism to analyze chemical reaction
networks, \textsl{Mol.\ Inform.\  }\textbf{29} (2010), 838--843. 
\href{https://doi.org/10.1002/minf.201000086}{https://doi.org/10.1002/minf.201000086}.

@@

@@

@@

\bibitem{SSV} P.\ Schultz, D.\ Spivak and C.\ Vasilakopoulou, Dynamical systems and sheaves, \textsl{Appl.\ Cat.\ Struct.\ }\textbf{28} (2020), 1--57. 
\href{https://doi.org/10.1007/s10485-019-09565-x}{https://doi.org/10.1007/s10485-019-09565-x}.
Available as \href{https://arxiv.org/abs/1609.08086}{arXiv:1609.08086}.

@@

\bibitem{Wilkinson} D.\ J.\ Wilkinson, \textsl{Stochastic Modelling for Systems Biology},
Taylor and Francis, New York, 2006. \href{https://doi.org/10.1201/b11812}{https://doi.org/10.1201/b11812}.

\bibitem{Willems} J.\ C.\ Willems, The behavioral approach to open and interconnected systems, \textsl{IEEE Control Systems Magazine} \textbf{27} 
(2007), 46--99. \href{https://doi.org/10.1109/MCS.2007.906923}{https://doi.org/10.1109/MCS.2007.906923}.
